Notes

### 2020-02-24 Notes/Notes.tex
some qubo re-scale discussion in Notes
added a few words

>>>>

\section{re-scale QUBO using ancillary qubits?}

Original qubo is
\begin{equation}
f= \psi^T Q \psi .
\end{equation}
We can re-scale Q by a factor of 2 like:
 \begin{align}
\psi_2 &= (\psi , \psi)^T \\
Q_2 &= 
\begin{pmatrix}
\frac{Q}{2} & 0 \\
0 & \frac{Q}{2} \\
\end{pmatrix} .
\end{align}
Then we have the re-scaled qubo:
\begin{align}
f &= \psi_2^T Q_2 \psi_2 \\
&=  \psi^T  \frac{Q}{2} \psi +  \psi^T  \frac{Q}{2} \psi \\
&=  \psi^T Q \psi .
\end{align}
The re-scaled qubo in general is
 \begin{align}
\psi_2 &= (\psi_a , \psi_b)^T \\
Q_2 &= 
\begin{pmatrix}
\frac{Q}{2} & 0 \\
0 & \frac{Q}{2} \\
\end{pmatrix} .
\end{align}
\begin{align}
f &= \psi_2^T Q_2 \psi_2 \\
&=  \psi_a^T  \frac{Q}{2} \psi_a +  \psi_b^T  \frac{Q}{2} \psi_b .
\end{align}
This function reaches the maximum if and only if both $\psi_a$ and $\psi_b$ are in the solution space.
